Networked Character Devices

### 2011-12-07 report/paper.tex
Added LaTeX Listings support and sample to paper and presentation

\usepackage[text={6in, 9in}, centering]{geometry}
\usepackage{graphicx}
\usepackage{url}

@@

@@

>>>>

\usepackage[text={6in, 9in}, centering]{geometry}
\usepackage{graphicx}
\usepackage{url}
\usepackage{listings}

@@

\lstloadlanguages{C}
\lstset{
  language=C,
  basicstyle=\footnotesize,
  numbers=none,
  numberstyle=\footnotesize,
  stepnumber=1,
  numbersep=5pt,
  showspaces=false,
  showstringspaces=false,
  showtabs=false,
  tabsize=4,
  captionpos=b,
  breaklines=true,
  breakatwhitespace=false,
  title=\lstname,
  frame=single,
  frameround=tttt
}

@@

\lstinputlisting[float=*,
  caption={Listing Code Sample},
  label=lst:codeSample.c]{codesample.c}
